---
title: "Untitled"
author: "Zachary M. Smith"
date: "2/13/2020"
output: html_document
---

# Diversity Metrics

Diversity metric in general combine the measure of taxonomic evenness and taxonomic richness.
A number of diversity metrics can be calculated using `taxa_div()`: 

1. _Shannon-Wiener Diversity_ ("shannon")
2. _Simpson's Diversity_ ("simpson")
3. _Margalef's Diversity_ ("margalef")
4. _Menhinick's Diversity_ ("menhinick")
5. _Pielou Evenness_ ("pielou")

## Community Diversity

```{r div_comm}
div.df <- nest.df %>% 
  dplyr::mutate(
    shannon_genus = taxa_div(.dataframe = .,
                             .key_col = uid,
                             .counts_col = total,
                             .group_col = genus,
                             .job = "shannon",
                             .base_log = 2,
                             .unnest_col = data),
    simpson_genus = taxa_div(.dataframe = .,
                             .key_col = uid,
                             .counts_col = total,
                             .group_col = genus,
                             .job = "simpson",
                             .unnest_col = data),
    margalef_genus = taxa_div(.dataframe = .,
                              .key_col = uid,
                              .counts_col = total,
                              .group_col = genus,
                              .job = "margalef",
                              .unnest_col = data),
    menhinick_genus = taxa_div(.dataframe = .,
                               .key_col = uid,
                               .counts_col = total,
                               .group_col = genus,
                               .job = "menhinick",
                               .unnest_col = data),
    pielou_genus = taxa_div(.dataframe = .,
                            .key_col = uid,
                            .counts_col = total,
                            .group_col = genus,
                            .job = "pielou",
                            .unnest_col = data)
  )
```

```{r div_comm_tbl, echo=FALSE}
standard_dt(div.df)
```

## Subset Diversity

```{r div_sub}
sub_div.df <- nest.df %>% 
  dplyr::mutate(
    simpson_gen_ept = taxa_div(.dataframe = .,
                            .key_col = uid,
                            .counts_col = total,
                            .group_col = genus,
                            .filter = order %in% c("ephemeroptera",
                                                   "plecoptera",
                                                   "trichoptera"),
                            .job = "simpson",
                            .unnest_col = data))
```

```{r div_sub_tbl, echo=FALSE}
standard_dt(sub_div.df)
```