---
title: "Untitled"
author: "Zachary M. Smith"
date: "2/13/2020"
output: html_document
---

# Abundance and Relative Abundance (%) Metrics

Abundance refers to the total count of all taxa observed during a sampling event. We can apply a filter to this metric as well to focus on specific aspects of the community, such as the abundance of EPT.

```{r abun_comm}
nest.df <- nest.df %>% 
  dplyr::mutate(
    abundance = taxa_abund(.,
                           .key_col = unique_id,
                           .counts_col = reporting_value),
    abund_ept = taxa_abund(.,
                           .key_col = unique_id,
                           .counts_col = reporting_value,
                           .filter = order %in% c("ephemeroptera",
                                                  "plecoptera",
                                                  "trichoptera"))
  )
```

```{r abund_comm_tbl, echo=FALSE}
standard_dt(nest.df)
```

## Subset Relative Abundance (%)

Generally, abundance metrics are better represented on a normalized scale. Calculating the relative abundance (percentage) of a subset metrics should provide a more robust measure than raw abundance measures.

```{r rel_abund}
nest.df <- nest.df %>% 
  dplyr::mutate(
    pct_ephemeroptera = taxa_pct(.data = .,
                                  .key_col = unique_id,
                                  .counts_col = reporting_value,
                                  .filter = order %in% "ephemeroptera"),
    pct_ept = taxa_pct(.data = .,
                        .key_col = unique_id,
                        .counts_col = reporting_value,
                        .filter = order %in% c("ephemeroptera",
                                                   "plecoptera",
                                                   "trichoptera"))
  )
```

```{r rel_abund_tbl, echo=FALSE}
standard_dt(nest.df)
```
